### 2024-12-16 README.Rmd
update logo
fix typo

# hatchR <a href="https://bmait101.github.io/hatchR/"><img src="man/figures/logo.png" alt="hatchR website" align="right" height="139"/></a>

@@

If you use **hatchR** in a formal publication or report, please cite it. Citing **hatchR** lets us devote more resources to it in the future. View the **hatchR** citation by running

>>>>

# hatchR <a href="https://bmait101.github.io/hatchR/"><img src="man/figures/logo.png" align="right" height="139" alt="hatchR website" /></a>

@@

If you use **hatchR** in a formal publication or report, please cite it. Citing **hatchR** lets us devote more resources to it in the future. View the **hatchR** citation by running:
